%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Template
% Version 1. (19/06/2020)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % !TEX program = xelatex
\documentclass[]{rajnikant-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Rajnikant}{Raman}{ 
	\urlstyle{same}\url{http://rajnikant7008.github.io} | Stockholm, Sweden \\
\href{mailto:rajnikant7008@gmail.com}{rajnikant7008@gmail.com} | +91-9631419656, +46-760009855
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{National Institute of Technology}
\descript{B.Tech in Information Technology}
\location{Cum. GPA: 9.12, Rank: 1}
\location{ July 2011 - May 2015 | Patna, India}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/rajnikant7008}{\custombold{rajnikant7008}} \\
LinkedIn:  \href{https://www.linkedin.com/in/rajnikant7008}{\custombold{rajnikant7008}} \\
Twitter: \href{https://twitter.com/rajnikant7008}{\custombold{rajnikant7008}} \\
Skype:  {\custombold{rajnik914}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Java \textbullet{}  Python \textbullet{} SQL \textbullet{} Kotlin \\ 
Bash \textbullet{} AngularJS \textbullet{} React JS 
\sectionsep

\subsection{Technologies}
 Terraform   \textbullet{}  Docker \textbullet{}  Kafka  \\
 RESTful Web Services \textbullet{} Splunk \\
 Hadoop
 \sectionsep
 
\location{Framework}
  Dropwizard \textbullet{} Spring Boot \\ 
 MapReduce  \textbullet{} Hibernate
\sectionsep

\location{Databases}
 PostgreSQL \textbullet{}Cassandra \\
  MySQL \textbullet{} MongoDB \textbullet{} Aerospike \\
   Elasticsearch \textbullet{} Vertica
 \sectionsep
 
 \location{Amazon Web Services}
 \sectionsep
 
   \location{Google Cloud Platform}
  \sectionsep
 
 \location{Tools}
      Maven \textbullet{} Tomcat \textbullet{} Git \\
       Scikit-Learn  \textbullet{} IntelliJ IDEA \\
      Postman \textbullet{} cTAKES \textbullet{} JMeter 
\sectionsep



\section{Coursework}
\subsection{Undergraduate}
Operating Systems \\
Artificial Intelligence + Practicum \\
Distributed Systems \\
Data Structures and Algorithms\\
Unix Systems 
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{\href{https://www.izettle.com/}{PayPal}}
\descript{| Backend Developer}
\location{May 2019 - Present | Stockholm, Sweden}
\begin{tightemize}
	\item  Building and maintaining services that assess risk when we onboard merchants, when they take business loans, as well as in the daily use of our products. 
\end{tightemize}
\sectionsep

\runsubsection{\href{https://www.bankbazaar.com}{BankBazaar}}
\descript{| Senior Software Engineer }
\location{ Dec 2016 – May 2019 | Bengaluru, India}
\begin{tightemize}
\item \custombold{Personalization:}  Designed and developed services to ingest millions of customer data across the platform on a
real-time basis and unite them into a single profile per customer for recommendation engine.
\item \custombold{Data Warehousing:} Setup, schema design and management of Analytics DB. Built an internal engine to
access the data using a web interface. Bulk data processing with Hadoop for daily ETL injection into Amazon Redshift.

\end{tightemize}
\sectionsep


\runsubsection{\href{https://www.snapdeal.com}{Snapdeal}}
\descript{| Software Engineer}
\location{July 2015 - Nov 2016 | Bengaluru, India}
\begin{tightemize}
\item Built machine learning system to set up the ranking mechanism of products. 
\item Developed highly scalable APIs  to cater several clients of user generated content.
\item Designed and built dashboard for the moderation  and search of the user generated content.
\end{tightemize}
\sectionsep

\runsubsection{Indian Institute of Technology}
\descript{| Research Intern}
\location {May 2014 - July 2014 | Patna, India}
\begin{tightemize}
\item  \custombold{Analysis of Clinical Text:} Designed and implemented an intelligent system for disorder mention detection from
patient records by combining supervised methods for text analysis with unsupervised ones. The purpose of this
task was to enhance current research in NLP methods used in the clinical domain.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\location{Privacy Enhancement in Email Clients}
Designed and tweaked an open source E-mail client to improve privacy features in web mail clients from both sender and receiver perspective.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\textbullet{}  \href{https://rd.springer.com/chapter/10.1007/978-3-319-32467-8_118}{ \custombold{Privacy Enhancement in E-Mail Clients:}} Published by Springer International \\ \hspace{9pt}Publishing Switzerland. \\
\textbullet{}  \custombold{Product Quality Prediction in a Large E-commerce Environment:} Published \\ \hspace{8pt} as White Paper at Snapdeal.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
\sectionsep
\begin{tightemize}
	\item  Honored with Gold Award from Snapdeal for excellence, innovation, quality and growth.
	\item Sole recipient of Director's Gold Medal at undergraduate level, NIT Patna.
	\item Winner of Algo-Z-Ripper (Annual coding competition at NIT Patna).
	\item Runner up in WebWeaver (Annual web designing competition at NIT Patna).
	\item Served as core team member of official Web Development Team at NIT Patna.
	\item Winner of science quiz at district level organised by Indian Culture Knowledge Haridwar.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage} 
\end{document}  \documentclass[]{article}