%% One-page resume — Rajnikant Raman (ATS-optimized, single-column)
\documentclass[9pt,a4paper]{article}

\usepackage[top=0.35in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}

\definecolor{dark}{RGB}{30,30,30}
\definecolor{mid}{RGB}{90,90,90}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}
\color{dark}

%% Section headings
\titleformat{\section}
  {\small\bfseries\scshape}{}{0em}{}[\vspace{-5pt}\rule{\linewidth}{0.4pt}]
\titlespacing{\section}{0pt}{4pt}{2pt}

%% Bullet lists
\setlist[itemize]{
  leftmargin=12pt, topsep=1pt, itemsep=0.5pt,
  parsep=0pt, label=\textbullet
}

% ═══════════════════════════════════════════
\begin{document}

%% ── HEADER ───────────────────────────────
\begin{center}
  {\LARGE\bfseries Rajnikant Raman}\\[2pt]
  {\small Engineering Manager \textbar\ FinTech \& Payments \textbar\ Amsterdam, Netherlands}\\[2pt]
  {\small
    \href{mailto:rajnikant7008@gmail.com}{rajnikant7008@gmail.com}
    | +31 627273340
    | \href{https://rajnikant7008.github.io}{rajnikant7008.github.io}
    | \href{https://linkedin.com/in/rajnikant7008}{linkedin.com/in/rajnikant7008}
  }
\end{center}

\vspace{2pt}

%% ── SUMMARY ──────────────────────────────
\section{Summary}
{\small Engineering leader with 11+ years building mission-critical payment systems at global scale. Track record of scaling platforms 50x, hiring and growing high-performing teams, and establishing org-wide engineering culture and standards. Skilled in performance management, OKR-driven planning, technical strategy, and aligning engineering with business outcomes across product, commercial, and partner stakeholders.}

%% ── EXPERIENCE ───────────────────────────
\section{Experience}

\textbf{\href{https://www.adyen.com}{Adyen}} -- Engineering Manager \hfill Jul 2022 -- Present\\
{\small\color{mid} Amsterdam, Netherlands | Senior Engineer to Engineering Manager, promoted within 8 months}
\begin{itemize}
  \item Lead IPP Scalability team of 6 engineers, scaling platform 50x -- enabling 1M+ concurrent connections with latency under 100ms for global merchants across millions of devices.
  \item Grow engineers through hands-on hiring, performance management, and structured mentorship -- building an engineering culture of ownership, career development, and clear progression at all levels.
  \item Own cross-functional technical strategy across product, commercial and partner stakeholders -- translating business goals into engineering roadmaps and delivery commitments.
  \item Establish org-wide engineering standards -- defining ways of working, quality benchmarks and developer experience practices across the organization.
\end{itemize}

\vspace{1pt}
\textbf{\href{https://www.zettle.com/gb}{Zettle by PayPal}} -- Senior Backend Developer \hfill May 2019 -- Jun 2022\\
{\small\color{mid} Stockholm, Sweden}
\begin{itemize}
  \item Delivered compliance solutions supporting migration of millions of merchants across Europe in response to regulatory and banking license changes.
  \item Developed KYC/KYB risk systems for merchant onboarding and activity monitoring, improving detection of high-risk events and platform security.
  \item Evolved compliance platform architecture using Java, AWS and event-driven design to deliver scalable, secure backend systems.
\end{itemize}

\vspace{1pt}
\textbf{\href{https://www.bankbazaar.com}{BankBazaar}} -- Senior Software Engineer \hfill Dec 2016 -- May 2019\\
{\small\color{mid} Bangalore, India}
\begin{itemize}
  \item Architected a customer data platform using Java, Kafka and Cassandra -- processing millions of real-time events to build unified customer profiles, powering personalization and recommendation capabilities.
  \item Built org-wide ETL pipelines processing tens of millions of events, enabling enterprise reporting and data-driven decision-making.
  \item Mentored engineers and drove cross-team alignment on platform design and data architecture decisions.
\end{itemize}

\vspace{1pt}
\textbf{\href{https://www.snapdeal.com}{Snapdeal}} -- Software Engineer \hfill Jul 2015 -- Nov 2016\\
{\small\color{mid} Bangalore, India}
\begin{itemize}
  \item Built end-to-end ML pipeline for product ranking -- data pre-processing, feature extraction, model training and real-time prediction -- enhancing discovery across high-traffic e-commerce.
  \item Built scalable UGC platforms and APIs serving 5K+ TPS with p99 latency under 10ms.
\end{itemize}

%% ── SKILLS ───────────────────────────────
\section{Skills}
\textbf{Leadership:} Technical Strategy, Org Design, Team Scaling, Hiring, Performance Management, Engineering Culture, OKR Planning, Talent Development, Stakeholder Management, Operational Excellence\\[1pt]
\textbf{Technical:} Java, Python, Kotlin, Go, Spring Boot, Dropwizard, Terraform, Pulumi, Docker, Kubernetes, Nomad\\[1pt]
\textbf{Data \& Infrastructure:} Kafka, RabbitMQ, PostgreSQL, CockroachDB, Cassandra, Redis, MongoDB, Elasticsearch, Grafana, Splunk\\[1pt]
\textbf{Cloud \& Architecture:} AWS, Google Cloud Platform, Distributed Systems Design, WebSocket, Real-time Streaming

%% ── ACHIEVEMENTS ─────────────────────────
\section{Achievements}
\begin{itemize}
  \item \textbf{Speaker, Adyen Annual Conference 2025} -- Presented Public Cloud vision to 1,500+ attendees.
  \item \textbf{PayPal Spot Award 2021} -- Led European compliance migration across multiple stakeholder teams.
  \item \textbf{Snapdeal Gold Award 2016} -- Built end-to-end ML product ranking pipeline.
  \item \textbf{Director's Gold Medal 2015} -- Ranked 1st in B.Tech, NIT Patna, GPA 9.12.
\end{itemize}

%% ── EDUCATION ────────────────────────────
\section{Education}
\textbf{\href{https://www.nitp.ac.in/}{National Institute of Technology, Patna}} -- B.Tech, Information Technology \hfill Jul 2011 -- May 2015\\
{\small GPA: 9.12 | Rank: 1 | Director's Gold Medal}

%% ── PUBLICATIONS ─────────────────────────
\section{Publications}
\begin{itemize}
  \item \href{https://rd.springer.com/chapter/10.1007/978-3-319-32467-8_118}{\textbf{Privacy Enhancement in E-Mail Clients}} -- Springer International Publishing Switzerland, 2016.
  \item \textbf{Product Quality Prediction in a Large E-commerce Environment} -- Internal Research, Snapdeal, 2016.
\end{itemize}

\end{document}
