%% One-page resume — Rajnikant Raman (Human-reader, premium version)
\documentclass[9pt,a4paper]{article}

\usepackage[top=0.45in, bottom=0.4in, left=0.55in, right=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}
\usepackage{microtype}
\linespread{1.06}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[framemethod=none]{mdframed}

\definecolor{dark}{RGB}{81,83,89}
\definecolor{mid}{RGB}{126,129,139}
\definecolor{soft}{RGB}{103,105,112}
\definecolor{accent}{RGB}{63,108,182}
\definecolor{lightbg}{RGB}{251,252,254}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}
\color{dark}

%% Section headings
\titleformat{\section}
  {\small\scshape\bfseries\color{accent}}{}{0em}{}[\vspace{-5pt}{\color{accent}\rule{\linewidth}{0.5pt}}]
\titlespacing{\section}{0pt}{3pt}{2pt}

%% Bullet lists — accent-colored bullets
\setlist[itemize]{
  leftmargin=9pt, topsep=1pt, itemsep=1.5pt,
  parsep=0pt, label={\color{mid}\textbullet}
}

%% Summary box style — left accent border
\mdfdefinestyle{summarybox}{%
  leftline=true, rightline=false, topline=false, bottomline=false,
  linewidth=2pt, linecolor=accent,
  backgroundcolor=lightbg,
  innerleftmargin=8pt, innerrightmargin=4pt,
  innertopmargin=3pt, innerbottommargin=3pt,
  skipabove=2pt, skipbelow=2pt
}

%% ── Helpers ──────────────────────────────
\newcommand{\skill}[2]{%
  \noindent{\textbf{\small #1}}\newline
  \noindent{\footnotesize\setlength{\parskip}{0pt}#2}%
  \par\vspace{2.5pt}%
}

\newcommand{\employer}[5]{%
  \href{#5}{\textbf{#1}} \textbar\ {\small\scshape #2} \hfill {\small #3}\\[-1pt]
  {\small\color{mid} #4}%
}

% ═══════════════════════════════════════════
\begin{document}

%% ── HEADER ───────────────────────────────
\begin{center}
  {\fontsize{20}{22}\selectfont\bfseries Rajnikant Raman}\\[2pt]
  {\small\color{accent} Engineering Manager \textbar\ FinTech \& Payments \textbar\ Amsterdam}\\[3pt]
  {\footnotesize\color{mid}
    \href{https://rajnikant7008.github.io}{rajnikant7008.github.io}
    \textbar\ \href{mailto:rajnikant7008@gmail.com}{rajnikant7008@gmail.com}
    \textbar\ +31 627273340
    \textbar\ \href{https://linkedin.com/in/rajnikant7008}{LinkedIn}
    \textbar\ \href{https://github.com/rajnikant7008}{GitHub}
  }
\end{center}

\vspace{1pt}

%% ── SUMMARY ──────────────────────────────
\begin{mdframed}[style=summarybox]
{\small\color{soft} Engineering leader with 11+ years building mission-critical payment systems at global scale. Track record of scaling platforms {\color{accent}50x}, hiring and growing high-performing teams, and establishing org-wide engineering culture and standards. Focused on aligning technical strategy with business outcomes and scaling engineering organizations across FinTech \& Payments.}
\end{mdframed}

\vspace{1pt}

%% ── TWO COLUMNS ──────────────────────────
\noindent
\begin{minipage}[t]{0.285\textwidth}
\setlength{\parskip}{0pt}

%% LEFT — Skills
\section{Skills}
\vspace{2pt}

\skill{Leadership}{%
  Engineering Management\newline
  Technology Roadmapping\newline
  Organizational Scaling\newline
  Talent Development\newline
  Stakeholder Management\newline
  Operational Excellence%
}

\vspace{2pt}
\skill{Programming}{Java {\color{mid}\textperiodcentered} Python {\color{mid}\textperiodcentered} Kotlin {\color{mid}\textperiodcentered} Go}

\vspace{2pt}
\skill{Technical}{%
  Distributed Systems {\color{mid}\textperiodcentered} Real-time Streaming\newline
  Kafka {\color{mid}\textperiodcentered} RabbitMQ {\color{mid}\textperiodcentered} WebSocket\newline
  Cassandra {\color{mid}\textperiodcentered} Redis\newline
  PostgreSQL {\color{mid}\textperiodcentered} MongoDB\newline
  Terraform {\color{mid}\textperiodcentered} Docker\newline
  Kubernetes {\color{mid}\textperiodcentered} Nomad\newline
  AWS {\color{mid}\textperiodcentered} GCP\newline
  Grafana {\color{mid}\textperiodcentered} Splunk%
}

%% LEFT — Education
\vspace{5pt}
\section{Education}
{\small\textbf{\href{https://www.nitp.ac.in/}{NIT Patna}}}\newline
{\footnotesize B.Tech — Information Technology\newline
GPA: \textbf{9.12} \textbar\ Rank \textbf{1} \textbar\ \textit{Gold Medalist}\newline
Jul 2011 -- May 2015}

%% LEFT — Leadership Philosophy
\vspace{5pt}
\section{Philosophy}
\vspace{2pt}
{\footnotesize\color{soft}
Invest in people first ---\newline
great products follow.\par\vspace{3pt}
Build trust before you need it.\par\vspace{3pt}
Engineering excellence is a\newline
culture, not a checklist.\par\vspace{3pt}
Lead with clarity,\newline
especially in ambiguity.%
}

\end{minipage}%
\hfill%
%% ── RIGHT COLUMN ─────────────────────────
\begin{minipage}[t]{0.685\textwidth}
\setlength{\parskip}{0pt}

%% RIGHT — Experience
\section{Experience}

\employer{Adyen}{Engineering Manager}{Jul 2022 -- {\color{accent}\textbf{Present}}}{Amsterdam, Netherlands \textbar\ \textit{Senior Engineer \textrightarrow\ EM, promoted within 8 months}}{https://www.adyen.com}
\begin{itemize}
  \item Lead IPP Scalability team of {\color{accent}6 engineers}, owning platform strategy that scaled {\color{accent}50x} -- enabling 1M+ concurrent connections with sub-100ms latency across millions of devices globally.
  \item Hire, develop and retain talent -- structured mentorship, clear career frameworks, and performance management that grew engineers into senior technical contributors.
  \item Drive {\color{accent}cross-functional strategy} across product, commercial and partner stakeholders -- aligning engineering roadmaps with business outcomes and quarterly OKRs.
  \item Define {\color{accent}org-wide engineering standards} -- ways of working and quality benchmarks adopted across multiple teams.
\end{itemize}

\vspace{8pt}
\employer{Zettle by PayPal}{Senior Backend Developer}{May 2019 -- Jun 2022}{Stockholm, Sweden}{https://www.zettle.com/gb}
\begin{itemize}
  \item Led {\color{accent}cross-org compliance migration} -- coordinating legal, product and engineering to move millions of merchants under European regulatory changes.
  \item Owned KYC/KYB risk platform end-to-end -- scoping requirements with stakeholders, designing systems, and driving execution across {\color{accent}multiple team boundaries}.
  \item Mentored junior engineers and drove {\color{accent}architectural decision-making} for the compliance domain, establishing patterns adopted by adjacent teams.
\end{itemize}

\vspace{8pt}
\employer{BankBazaar}{Senior Software Engineer}{Dec 2016 -- May 2019}{Bangalore, India}{https://www.bankbazaar.com}
\begin{itemize}
  \item Led design and delivery of a customer data platform processing millions of real-time events -- driving {\color{accent}cross-team alignment} on a unified architecture that powered personalization across the product.
  \item Drove {\color{accent}org-wide data strategy} -- built ETL pipelines processing tens of millions of events, enabling executive reporting and data-driven prioritization.
  \item Mentored engineers across teams, led architecture reviews, and established {\color{accent}technical decision-making practices} that improved delivery predictability.
\end{itemize}

\vspace{8pt}
\employer{Snapdeal}{Software Engineer}{Jul 2015 -- Nov 2016}{Bangalore, India}{https://www.snapdeal.com}
\begin{itemize}
  \item Owned end-to-end ML pipeline for product ranking -- from problem framing through production deployment -- improving discovery metrics across high-traffic e-commerce.
  \item Built scalable UGC platforms and APIs serving 5K+ TPS with p99 latency under 10ms.
\end{itemize}

%% RIGHT — Publications
\section{Publications}
\begin{itemize}[itemsep=2pt]
  \item \href{https://rd.springer.com/chapter/10.1007/978-3-319-32467-8_118}{\textbf{Privacy Enhancement in E-Mail Clients}} \hfill {\small 2016}\\[-2pt]
  {\small\color{mid} Springer International Publishing Switzerland}
  \item \textbf{Product Quality Prediction in E-commerce} \hfill {\small 2016}\\[-2pt]
  {\small\color{mid} Internal Research, Snapdeal}
\end{itemize}

%% RIGHT — Achievements
\section{Achievements}
\begin{itemize}[itemsep=2pt]
  \item \textbf{Speaker,} Adyen Annual Conference 2025 {\small\color{mid}-- Presented Public Cloud vision to 1,500+ attendees.}
  \item \textbf{PayPal Spot Award,} 2021 {\small\color{mid}-- Led European compliance migration across multiple stakeholder teams.}
  \item \textbf{Snapdeal Gold Award,} 2016 {\small\color{mid}-- Built end-to-end ML product ranking pipeline.}
  \item \textbf{Director's Gold Medal,} 2015 {\small\color{mid}-- Ranked 1st in B.Tech, NIT Patna, GPA 9.12.}
\end{itemize}

\end{minipage}

\end{document}
